The NIME of the Title Is Hello

### 2025-01-15 src/main.tex
authors

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Ben Trovato}
\authornote{Both authors contributed equally to this research.}
\email{trovato@corporation.com}
\orcid{1234-5678-9012}
\author{G.K.M. Tobin}
\authornotemark[1]
\email{webmaster@marysville-ohio.com}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \city{Dublin}
  \state{Ohio}
  \country{USA}
}

\author{Lars Th{\o}rv{\"a}ld}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \city{Hekla}
  \country{Iceland}}
\email{larst@affiliation.org}

\author{Valerie B\'eranger}
\affiliation{%
  \institution{Inria Paris-Rocquencourt}
  \city{Rocquencourt}
  \country{France}
}

\author{Aparna Patel}
\affiliation{%
 \institution{Rajiv Gandhi University}
 \city{Doimukh}
 \state{Arunachal Pradesh}
 \country{India}}

\author{Huifen Chan}
\affiliation{%
  \institution{Tsinghua University}
  \city{Haidian Qu}
  \state{Beijing Shi}
  \country{China}}

\author{Charles Palmer}
\affiliation{%
  \institution{Palmer Research Laboratories}
  \city{San Antonio}
  \state{Texas}
  \country{USA}}
\email{cpalmer@prl.com}

\author{John Smith}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \city{Hekla}
  \country{Iceland}}
\email{jsmith@affiliation.org}

\author{Julius P. Kumquat}
\affiliation{%
  \institution{The Kumquat Consortium}
  \city{New York}
  \country{USA}}
\email{jpkumquat@consortium.net}

@@

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{Do, Not, Us, This, Code, Put, the, Correct, Terms, for,
  Your, Paper}
%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  \includegraphics[width=\textwidth]{src/images/side_w-o_sensors.jpeg}
  \caption{Two synthesisers on a table, 2019.}
  \Description{Enjoying looking at two synthesisers.
  A Korg Monotron and a Korg Volca FM.}
  \label{fig:teaser}
\end{teaserfigure}

>>>>

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Matthew Hamilton}
% \authornote{Both authors contributed equally to this research.}
\email{matthew.hamilton2@unibo.it}
\orcid{1234-5678-9012}
\author{Michele Ducceschi}
% \authornotemark[1]
\email{michele.ducceschi@unibo.it}
\affiliation{%
  \institution{Università di Bologna}
  \city{Bologna}  
  \country{Italy}
}

\author{Roberto Livi}
\author{Catalina Vincens}
\affiliation{%
  \institution{Museo San Colombano}
  \city{Bologna}
  \country{Italy}}

\author{Andrew McPherson}
\affiliation{%
 \institution{Imperial College}
 \city{London}
 \country{United Kingdom}}

@@

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{Do, Not, Us, This, Code, Put, the, Correct, Terms, for,
  Your, Paper}
%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  \includegraphics[width=\textwidth]{images/side_w-o_sensors.jpeg}
  \caption{3-key Model Harpsichord Mechanism by Graziano Bandini, Bologna 2023}
  \Description{3-key Model Harpsichord Mechanism by Graziano Bandini, Bologna 2023}
  \label{fig:teaser}
\end{teaserfigure}
